Novel Sampling Using Stochastic Gradient Descent

### 2016-12-05 poster/main.tex
final format

% \usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster
\usepackage[scale=0.8]{beamerposter}

@@

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
% \setlength{\paperwidth}{48in} % A0 width: 46.8in
% \setlength{\paperheight}{36in} % A0 height: 33.1in
\setlength{\paperwidth}{36in} % A0 width: 46.8in
\setlength{\paperheight}{24in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
% \setlength{\onecolwid}{0.22\paperwidth} % Width of one column
% \setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
% \setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\onecolwid}{0.3013\paperwidth} % Width of one column
\setlength{\twocolwid}{0.6026\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.904\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

@@

\begin{figure}
    \centering
    \includegraphics[width=.3\onecolwid]{../figure/case1_step_0.005_iter_1e3.png}
    \includegraphics[width=.3\onecolwid]{../figure/case1_step_0.005_iter_1e4.png}
    \includegraphics[width=.3\onecolwid]{../figure/case1_step_0.005_iter_1e5.png}\\
    \includegraphics[width=.3\onecolwid]{../figure/case2_step_0.005_iter_1e3.png}
    \includegraphics[width=.3\onecolwid]{../figure/case2_step_0.005_iter_1e4.png}
    \includegraphics[width=.3\onecolwid]{../figure/case2_step_0.005_iter_1e5.png}\\
    \includegraphics[width=.3\onecolwid]{../figure/case3_step_0.005_iter_1e3.png}
    \includegraphics[width=.3\onecolwid]{../figure/case3_step_0.005_iter_1e4.png}
    \includegraphics[width=.3\onecolwid]{../figure/case3_step_0.005_iter_1e5.png}
    \caption{Empirical stationary distribution using SGD. Different columns correspond to different samples sizes ($1e3$, $1e4$, and $1e5$). Different rows correspond to different distributions ($f_1(x) = \exp(-x^4)$, $f_2(x) = \exp(-(x^2 - 4)(x^2 - 1))$, $f_3(x) = \exp(-|x|)$.}
    \label{Fig:exp1}
\end{figure}

@@

\begin{itemize}
\item Proposed fast SGD sampler for posterior distributions when computing the likelihood using full data is intensive
\item Proved accurate stationary distribution based on oracle results
\item Established connection between SGD and maximize \emph{a posteriori} (MAP)
\item Derived upper bound on mixing time
\item Future work: Finite sample rates of convergence for the mixing time
\end{itemize}

>>>>

\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster
% \usepackage[scale=0.8]{beamerposter}

@@

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in} % A0 width: 46.8in
\setlength{\paperheight}{36in} % A0 height: 33.1in
% \setlength{\paperwidth}{36in} % A0 width: 46.8in
% \setlength{\paperheight}{24in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
% \setlength{\onecolwid}{0.22\paperwidth} % Width of one column
% \setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
% \setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\onecolwid}{0.3013\paperwidth} % Width of one column
\setlength{\twocolwid}{0.6026\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.904\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

@@

\begin{figure}
    \centering
    \includegraphics[width=.33\onecolwid]{../figure/case1_step_0.005_iter_1e3.png}
    \includegraphics[width=.33\onecolwid]{../figure/case1_step_0.005_iter_1e4.png}
    \includegraphics[width=.33\onecolwid]{../figure/case1_step_0.005_iter_1e5.png}\\
    \includegraphics[width=.33\onecolwid]{../figure/case2_step_0.005_iter_1e3.png}
    \includegraphics[width=.33\onecolwid]{../figure/case2_step_0.005_iter_1e4.png}
    \includegraphics[width=.33\onecolwid]{../figure/case2_step_0.005_iter_1e5.png}\\
    \includegraphics[width=.33\onecolwid]{../figure/case3_step_0.005_iter_1e3.png}
    \includegraphics[width=.33\onecolwid]{../figure/case3_step_0.005_iter_1e4.png}
    \includegraphics[width=.33\onecolwid]{../figure/case3_step_0.005_iter_1e5.png}
    \caption{Empirical stationary distribution using SGD. Different columns correspond to different samples sizes ($1e3$, $1e4$, and $1e5$). Different rows correspond to different distributions ($f_1(x) = \exp(-x^4)$, $f_2(x) = \exp(-(x^2 - 4)(x^2 - 1))$, $f_3(x) = \exp(-|x|)$.}
    \label{Fig:exp1}
\end{figure}

@@

\begin{itemize}
\item Proposed fast SGD sampler for posterior distributions when computing the likelihood using full data is intensive
\item Proved accurate stationary distribution based on oracle results
\item Established connection between SGD and maximize \emph{a posteriori}
\item Derived upper bound on mixing time
\item Future work: Finite sample rates of convergence for the mixing time
\end{itemize}
